\begin{singlespacing}
It is difficult to narrow down who to thank for helping me get to this point in my career, but I'll do my best to do so here.

First, I want to thank my advisor, Prathap Ramamurthy, for taking me on as a student and encouraging me to pursue research that was beyond my expertise at the time I came in. His support and investment in me has helped me grow and successfully transition back into academia after having left to pursue a career in industry. Moreover, he helped foster my path into atmospheric science from mechanical engineering, which has been tremendously helpful and supportive of my interests. Additionally, I would like to thank the NOAA-CESSRST program for funding my studies and research, as well as with providing me with a social and professional network that I am privileged to have.

I would not be able to write this thesis had it not been for the professors and mentors I have had the privilege to know. To Haoxiang Luo - you gave me my first opportunity to conduct research and exposed me to a career path I had no prior knowledge of. I would also like to thank Taehun Lee for being an excellent professor for multiple classes during my time at City College and for being invested in my growth as a student during and beyond my time here. I am grateful for two professors in the City College Earth and Atmospheric Sciences Department; Jimmy Booth and Johnny Luo. You are both outstanding instructors and your investment in your students inside and outside of the classroom, and your passion for atmospheric science helped further convince me to pursue research in the field.

I want to thank the friends I have made in my time since I left Vanderbilt - Veeshan Narinesingh, Harold Gamarro, and Omar Addasi - for your support and friendship throughout my time here. Being able to share the good and the bad of experiences throughout this program with you made the good times better, and the bad all the more bearable. I would also like to thank Bob Defelicé from my time at Collins Aerospace - working alongside you pushed me to be a better engineer, a better communicator, not take things too seriously, but most importantly, to question everything.

To Luis Antonetti and Richard Gomez - you have been inextricable parts of my life for so long and I am so lucky to have you to reach out to for any reason. You are two of the sharpest people I know, and I can always count on you to keep me on my toes, challenge me, and help me grow. I would also like to thank my friends and colleagues from my time at Vanderbilt - Jered Dominguez-Trujillo, Soobeen Park, Abel Yosef, Bo Kennedy, Austin Hardcastle, Dennis Sohn, and Elizabeth Lee. Without you, I don't think I could have made it through those four years without you. Your support, advice, and friendship were as invaluable to me then as they continue to be as I write this.

Tiff, you've been my partner through good and bad, highs and lows, and everything in between. You put up with me as I prepared draft after draft of my papers, and your patience with me never wore thin as I bored you with all the math and science behind my work. You helped convince me to pursue this transition back to school to go after the things I was passionate about, and for that, I'm forever indebted. Your support, love, and companionship are more than anything I can ask for.

Lastly, I would like to thank my family. David - you have brought laughter and lightheartedness with you to New York and I am beyond fortunate to have you around. Thanks for making my time here all the better. Mom, Pops, and Abuela - gracias por todo que han hecho por apoyarme en mis estudios. Aunque mis estudios han sido a una distancia, espero que se han sentido como parte de mi paso académico. Sin ustedes, no podría haber tenido todas las oportunidades que he tenido el privilegio de tener. Nunca voy a poder repagarlos por los sacrificios que han hecho por David y yo, pero espero que esta obra sea un símbolo de mi gratitud y mi esfuerzo de tomar ventaja del trabajo que han pasado. Esto es para ustedes. 

\vskip 1in
\end{singlespacing}

\noindent
Gabriel Angel Rios\\
May 25, 2022